---
title: "Coursera - Programming Assignment 2"
author: "Magdalena Schramel"
date: "11/4/2020"
output: html_document
---

<br></br>

##### **Put comments here that give an overall description of what your functions do**  

##### **Comment 1**  
Closures get their name because they enclose the environment of the parent function and can access all its variables. mX and inverseMX are stored in the environment in which they were defined. That means the enclosing environment of the get set functions returned by makeCacheMatrix().   

##### **Comment 2**  
Calculation of matrix inversion is memory intensive. It is therefore a good idea to cache the results of such calculation and have them available for further use.   

```{r}
## install.packages("Matrix")
library(Matrix)
## solve() function is in the Matrix package
## https://www.rdocumentation.org/packages/Matrix/versions/0.3-26/topics/solve.Matrix
```

<br></br>

##### **Write a short comment describing makeCacheMatrix() function**   

##### **Comment 3**    
The return value of this function is a list of the four functions:  
1. setMatrix()  
2. getMatrix()  
3. setInverseMatrix()  
4. getInverseMatrix()   

```{r}
makeCacheMatrix <- function(mX = matrix()) {
  
  inverseMX <- NULL
  
  setMatrix <- function(mX1) {
    mX <<- mX1
    inverseMX <<- NULL
  }
  
  getMatrix <- function() {
    mX
  }
  
  setInverseMatrix <- function(inverseMX1){ 
    inverseMX <<- inverseMX1
  }
  
  getInverseMatrix = function() {
    inverseMX
  }
  
  list(setMatrix = setMatrix, 
       getMatrix = getMatrix, 
       setInverseMatrix = setInverseMatrix,
       getInverseMatrix = getInverseMatrix)
}  

```

<br></br>

```{r}
cacheSolve <- function(mX, ...) {
  
  ## checking if the inverse matrix has been already calculated and is available in cache
  ## if yes, return the existing matrix
  inverseMX <- mX$getInverseMatrix()
  if(!is.null(inverseMX)){
    return(inverseMX)
  }
  
  ## inverse matrix is not available in cache
  ## calculate the inverse matrix
  else{		
    inverseMX <- solve(mX$getMatrix())
  } 
  
  ## set the value of the inverse matrix in cache
  mX$setInverseMatrix(inverseMX)
    
  return(inverseMX)
}
```

<br></br>

##### **Testing function makeCacheMatrix()**

```{r}
## Testing:
testMatrix1 <- matrix(rnorm(1:9), 3)
testMatrix1
cacheStatus <- makeCacheMatrix(testMatrix1)
testMatrix2 <- cacheSolve(cacheStatus)
testMatrix2
```

##### **Conclusion: test passed**

<br></br>

***
